IALE 2015 Analysis

### 2015-07-11 iale2015_sem.Rmd
Path analysis of 2005 & 2014 data for IALE 2015 World Congress presentation. I still need to do further data prep in order to achieve a repeated measures analysis. Considering limiting to data that I have measures for each sampling year

stems <- stems %>% select(-X) %>% filter(status == "Alive" | status == "Dead")
unique(stems$species)
stems$species <- tolower(stems$species)
stems$species[stems$species == "quke x quag"] <- "quag x quke"
stems$plotid <- tolower(stems$plotid)
stems %>% group_by(plotid, year) %>% summarise(tagged_rich = length(unique(species)))

os_richness <- left_join(
      stems %>% group_by(plotid, year) %>% summarise(tagged_rich = length(unique(species))),
      untagged_dbh %>% group_by(plotid, year) %>% summarise(untagged_rich = length(unique(species))), by = c("plotid", "year")
) %>% mutate(os_rich = tagged_rich + untagged_rich)
os_richness

@@

```{r join richness data}
plots_umca
richness
plots_umca <- rename(plots_umca, plotid = plot)
plots_umca$plotid <- tolower(plots_umca$plotid)

@@

>>>>

stems <- stems %>% select(-X) %>% filter(status == "Alive" | status == "Dead")
unique(stems$species)
stems$species <- tolower(stems$species)
stems$species[stems$species == "quke x quag"] <- "quag x quke"
stems$plotid <- tolower(stems$plotid)

tagged_dbh <- stems %>% filter(status == "Alive") %>% group_by(plotid, year, species) %>% summarise(live_count = length(species))
unique(tagged_dbh$species)
os_richness <- rbind(tagged_dbh, select(untagged_dbh, plotid, species, year, live_count))

os_richness <- left_join(
      stems %>% filter(year == 2005 | year == 2014) %>% group_by(plotid, year) %>% summarise(tagged_rich = length(unique(species))),
      untagged_dbh %>% group_by(plotid, year) %>% summarise(untagged_rich = length(unique(species))), by = c("plotid", "year")
) %>% mutate(os_rich = rowSums(cbind(tagged_rich,untagged_rich), na.rm = T))
os_richness

@@

```{r join richness and umca data}
plots_umca
richness
plots_umca <- rename(plots_umca, plotid = plot)
plots_umca$plotid <- tolower(plots_umca$plotid)

@@

## Path Analysis Oak Infection 2005

Here I am using the `oak_sod` data set which will be the oak infection (binomial) as the terminal response variable.

```{r oak_sod path model 2005}
library(ggm)
names(oak_sod)
oak_path1 <- DAG(
      tmi ~ elevation,
      os_rich ~ tmi,
      hrs_14_20 ~ elevation + d2c + avg_psi + tmi,
      tot_lfct ~ hrs_14_20 + os_rich + d2c,
      inf_oak_ct ~ tot_lfct + os_rich + hrs_14_20 + d2c
      )
isAcyclic(oak_path1)
bu_oak_path1 <- basiSet(oak_path1)
bu_oak_path1

oak_2005 <- filter(oak_sod, year == 2005)
summary(oak_2005)
oak_2005 <- select(oak_2005, plotid, uninf_oak_ct, inf_oak_ct, tot_lfct, hrs_14_20, elevation, tmi, avg_psi, os_rich, d2c)
oak_2005$tot_lfct[is.na(oak_2005$tot_lfct)] <- 0
filter(oak_2005, is.na(os_rich))
oak_2005 <- na.omit(oak_2005)
oak_2005$plotid <- as.factor(oak_2005$plotid)

# This model makes Gaussian assumptions, which should be incorrect for these data
shipley.test(oak_path1, cov(select(oak_2005, elevation, tmi, os_rich, hrs_14_20, d2c, avg_psi, tot_lfct, inf_oak_ct)), n = 170)
# The p-value of 0.1114 indicates that there is no severe violation of the conditional independence assumptions with the application of a Gaussian model
```

~~Violation of conditional independence supports addressing the complexity of the data using different model distributions to deal with the data.~~

Still I am going to fully asses the conditional independence claims

```{r assess conditional independence claims 2005}
bu_oak_path1 # 15 independence claims means 15 models
library(nlme)
library(lme4)

f1 <- lme(avg_psi ~ d2c, data = oak_2005, random = ~1|plotid)
summary(f1) # p = 0.5091
f2 <- lme(avg_psi ~ elevation, data = oak_2005, random = ~1|plotid)
summary(f2) # p = 0.2013
f3 <- lme(avg_psi ~ tmi + elevation, data = oak_2005, random = ~1|plotid)
summary(f3) # tmi; p = 0.1982
f4 <- lme(os_rich ~ avg_psi + tmi, data = oak_2005, random = ~1|plotid)
summary(f4) # avg_psi; p = 0.1066
f5 <- lm(log1p(tot_lfct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005)
# f5 <- lme(log1p(tot_lfct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005, random = ~1|plotid)
# f5 <- glmer(tot_lfct ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2005, family = "poisson")
summary(f5) # avg_psi; p = 0.5993
# f6 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "binomial")
# f6 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "quasibinomial")
f6 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2005, family = "binomial")
summary(f6) # avg_psi; p = 0.08970
f7 <- lm(elevation ~ d2c, data = oak_2005)
# f7 <- lme(elevation ~ d2c, data = oak_2005, random = ~1|plotid)
summary(f7) # p = 0.03163
f8 <- lm(log(tmi) ~ d2c + elevation, data = oak_2005)
# f8 <- lme(log(tmi) ~ d2c + elevation, data = oak_2005, random = ~1|plotid)
summary(f8) # d2c; p = 0.4375
f9 <- lm(os_rich ~ d2c + tmi, data = oak_2005)
# f9 <- lme(os_rich ~ d2c + tmi, data = oak_2005, random = ~1|plotid)
summary(f9) # d2c; p = 0.997
f10 <- lm(os_rich ~ elevation + tmi, data = oak_2005)
# f10 <- lme(os_rich ~ elevation + tmi, data = oak_2005, random = ~1|plotid)
summary(f10) # elevation; p = 0.260

# f11 <- lm(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005)
# f11 <- lm(log1p(tot_lfct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005)
f11 <- glm(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005, family = "poisson")
chat <- deviance(f11)/df.residual(f11)
QAIC(update(f11, family = x.quasipoisson), chat = chat)
f11 <- glm(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2005, family = "quasipoisson")
# f11 <- lme(log1p(tot_lfct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), random = ~1|plotid, data = oak_2005)
# f11 <- glmer(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2005, family = "poisson")
summary(f11) # elevation; p = 0.353425

# f12 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "binomial")
# chat <- deviance(f12)/df.residual(f12)
# QAIC(update(f12, family = x.quasibinomial), chat = chat)
# f12 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "quasibinomial")
f12 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2005, family = "binomial")
summary(f12) # elevation; p = 0.45826

f13 <- lm(log1p(tot_lfct) ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2005)
# f13 <- lme(log1p(tot_lfct) ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2005, random = ~1|plotid)
# f13 <- glmer(tot_lfct ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2005, family = "poisson")
summary(f13) # tmi; p = 0.113050

# f14 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "binomial")
# chat <- deviance(f14)/df.residual(f14)
# QAIC(update(f14, family = x.quasibinomial), chat = chat)
# f14 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2005, family = "quasibinomial")

f14 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2005, family = "binomial")
summary(f14) # tmi; p = 0.67609

f15 <- lm(os_rich ~ hrs_14_20 + avg_psi + d2c + elevation + tmi, data = oak_2005)
# f15 <- lme(os_rich ~ hrs_14_20 + avg_psi + d2c + elevation + tmi, data = oak_2005, random = ~1|plotid)
summary(f15) # hrs_14_20; p = 0.355

# Calculate C-statistic
pvalues <- c(summary(f1)$tTable[2,5], summary(f2)$tTable[2,5], summary(f3)$tTable[2,5], summary(f4)$tTable[2,5], summary(f5)$coefficients[2,4], summary(f6)$coefficients[2,4], summary(f7)$tTable[2,5], summary(f8)$tTable[2,5], summary(f9)$tTable[2,5], summary(f10)$tTable[2,5], summary(f11)$coefficients[2,4], summary(f12)$coefficients[2,4], summary(f13)$coefficients[2,4], summary(f14)$coefficients[2,4], summary(f15)$tTable[2,5])

cstat <- -2 * sum(log(pvalues))
cstat
```
Given the C-statistic of 26.9 and that 2k degrees of freedom would be 30 I think that this meets the criteria for supporting the conditional independence claims. So, this supports my path model, now I need to run the models to produce estimates for the path coefficients. This is the model set that I need to get the estimated path coefficients:

      1. os_rich ~ tmi,
      2. hrs_14_20 ~ elevation + d2c + avg_psi + tmi,
      3. tot_lfct ~ hrs_14_20 + os_rich + d2c,
      4. infected oak ~ tot_lfct + os_rich + hrs_14_20 + d2c

```{r estimate path coefficients 2005}
# f0 <- fitted(mlme1, level = 0)# Values from population model
# f1 <- fitted(mlme1, level = 1)# Within beach fitted values

# fit1 <- lm(tmi ~ scale(elevation), data = oak_2005)
fit1 <- lm(log(tmi) ~ scale(elevation), data = oak_2005) # best model
# fit1 <- lme(log(tmi) ~ scale(elevation), data = oak_2005, random = ~1|plotid, method = "ML")
summary(fit1)
par(mfrow = c(2,2))
plot(fit1)

# fit2 <- lm(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2005)
# fit2 <- lme(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2005, random = ~1|plotid) # best model
fit2 <- glmer(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi) + (1|plotid), data = oak_2005, family = "poisson")
# fit2 <- glmer.nb(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi) + (1|plotid), data = oak_2005)
summary(fit2)
plot(fit2)

# fit3 <- lm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c), data = oak_2005)
fit3 <- lm(log1p(tot_lfct) ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c), data = oak_2005)
fit3 <- glm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c), data = oak_2005, family = "poisson")
(chat <- deviance(fit3) / df.residual(fit3))
x.quasipoisson<-function(...){
  res<-quasipoisson(...)
  res$aic<-poisson(...)$aic
  res
}
library(MuMIn)
QAIC(update(fit3, family = x.quasipoisson), chat = chat) # 178.3
fit3 <- glm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c), data = oak_2005, family = "quasipoisson") # best model
# fit3 <- glmer(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + (1|plotid), data = oak_2005, family = "poisson")
summary(fit3)

# fit4 <- lm((inf_oak_ct/(inf_oak_ct+uninf_oak_ct)) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c), data = oak_2005)
# par(mfrow = c(2,2))
# plot(fit4)

# fit4 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c), data = oak_2005, family = "binomial")
# (chat <- deviance(fit4) / df.residual(fit4))
# x.quasibinomial<-function(...){
#   res<-quasibinomial(...)
#   res$aic<-binomial(...)$aic
#   res
# }
# library(MuMIn)
# QAIC(update(fit4, family = x.quasibinomial), chat = chat)
# fit4 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c), data = oak_2005, family = "quasibinomial")
# summary(fit4)

fit4 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(d2c) + (1|plotid), data = oak_2005, family = "binomial") # best model
summary(fit4)

fit5 <- lm(os_rich ~ tmi, data = oak_2005); AIC(fit5)
# fit5 <- lme(os_rich ~ tmi, data = oak_2005, random = ~1|plotid)
summary(fit5)

# Trying to plot the fitted model by each group...
# f0 <- fitted(fit4, level = 0)
# f1 <- fitted(fit4, level = 1)
# 
# f0[I]
# 
# I <- order(oak_2005$tot_lfct) ; lfct <- sort(oak_2005$tot_lfct)
# plot(lfct, f0[I], lwd = 4, type = "l",
#      ylab = "oak infection", xlab = "total leaf count")
# for(i in 1:length(f1)){
#       x1 <- oak_2005$hrs_14_20[oak_2005$plotid == i]
#       y1 <- f1[oak_2005$hrs_14_20 == i]
#       K <- order(x1)
#       lines(sort(x1), y1[K], col = "red")
# }
# text(oak_2005$hrs_14_20, oak_2005$tot_lfct, oak_2005$plotid, cex = 0.9)
```

## Path Analysis Oak Infection - 2014
Now I am going to fit the same path model to data from 2011.

```{r oak_sod path model 2014}
oak_path1 <- DAG(
      tmi ~ elevation,
      os_rich ~ tmi,
      hrs_14_20 ~ elevation + d2c + avg_psi + tmi,
      tot_lfct ~ hrs_14_20 + os_rich + d2c,
      inf_oak_ct ~ tot_lfct + os_rich + hrs_14_20 + d2c
      )

oak_2014 <- filter(oak_sod, year == 2014)
oak_2014 %>% select(plotid, tagged_rich, untagged_rich, os_rich) %>%
      filter(is.na(os_rich))
summary(oak_2014)
oak_2014 <- select(oak_2014, plotid, uninf_oak_ct, inf_oak_ct, tot_lfct, hrs_14_20, hrs_blw10, hrs_abv25, elevation, tmi, avg_psi, os_rich, d2c)
oak_2014$tot_lfct[is.na(oak_2014$tot_lfct)] <- 0
oak_2014 <- na.omit(oak_2014)
oak_2014$plotid <- as.factor(oak_2014$plotid)

shipley.test(oak_path1, cov(select(oak_2014, elevation, tmi, os_rich, hrs_14_20, d2c, avg_psi, tot_lfct, inf_oak_ct)), n = 168)
# Strongly significant p-value

# shipley.test(DAG(
#       tmi ~ elevation,
#       os_rich ~ tmi,
#       hrs_blw10 ~ elevation + d2c + avg_psi + tmi,
#       tot_lfct ~ hrs_blw10 + os_rich + d2c,
#       inf_oak_ct ~ tot_lfct + os_rich + hrs_blw10 + d2c), 
#       cov(select(oak_2014, elevation, tmi, os_rich, hrs_blw10, d2c, avg_psi, tot_lfct, inf_oak_ct)), 
#       n = 168)
```

```{r assess conditional independence 2014}
f1 <- lme(avg_psi ~ d2c, data = oak_2014, random = ~1|plotid)
summary(f1) # p = 0.591
f2 <- lme(avg_psi ~ elevation, data = oak_2014, random = ~1|plotid)
summary(f2) # p = 0.2171
f3 <- lme(avg_psi ~ tmi + elevation, data = oak_2014, random = ~1|plotid)
summary(f3) # tmi; p = 0.1889
f4 <- lm(os_rich ~ avg_psi + tmi, data = oak_2014)
# f4 <- lme(os_rich ~ avg_psi + tmi, data = oak_2014, random = ~1|plotid)
summary(f4) # avg_psi; p = 0.156
f5 <- lm(log1p(tot_lfct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014)
# f5 <- lme(log1p(tot_lfct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, random = ~1|plotid)
# f5 <- glmer(tot_lfct ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2014, family = "poisson")
summary(f5) # avg_psi; p = 0.265

f6 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "binomial")
chat <- deviance(f6)/df.residual(f6)
QAIC(update(f6, family = x.quasibinomial), chat = chat)
f6 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "quasibinomial")
# f6 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(avg_psi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2014, family = "binomial")
summary(f6) # avg_psi; p = 0.000722

f7 <- lm(log(elevation) ~ d2c, data = oak_2014)
# f7 <- lme(log(elevation) ~ d2c, data = oak_2014, random = ~1|plotid)
summary(f7) # p = 0.0101

f8 <- lm(log(tmi) ~ d2c + elevation, data = oak_2014)
# f8 <- lme(log(tmi) ~ d2c + elevation, data = oak_2014, random = ~1|plotid)
summary(f8) # d2c; p = 0.65795

f9 <- lm(log1p(os_rich) ~ d2c + tmi, data = oak_2014)
# f9 <- lme(log1p(os_rich) ~ d2c + tmi, data = oak_2014, random = ~1|plotid)
summary(f9) # d2c; p = 0.73

f10 <- lm(log1p(os_rich) ~ elevation + tmi, data = oak_2014)
# f10 <- lme(log1p(os_rich) ~ elevation + tmi, data = oak_2014, random = ~1|plotid)
summary(f10) # elevation; p = 0.126

# f11 <- lm(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014)
f11 <- lm(log1p(tot_lfct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014)
f11 <- glm(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, family = "poisson")
chat <- deviance(f11)/df.residual(f11)
QAIC(update(f11, family = x.quasipoisson), chat = chat)
f11 <- glm((tot_lfct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, family = "quasipoisson")
# f11 <- lme(log1p(tot_lfct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich), random = ~1|plotid, data = oak_2014)
# f11 <- glmer(tot_lfct ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2014, family = "poisson")
summary(f11) # elevation; p = 0.0170

f12 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "binomial")
chat <- deviance(f12)/df.residual(f12)
QAIC(update(f12, family = x.quasibinomial), chat = chat)
f12 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "quasibinomial")
# f12 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(elevation) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2014, family = "binomial")
summary(f12) # elevation; p = 0.00627

f13 <- lm(log1p(tot_lfct) ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2014)
f13 <- glm(tot_lfct ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, family = "poisson")
chat <- deviance(f13)/df.residual(f13)
QAIC(update(f13, family = x.quasipoisson), chat = chat)
f13 <- glm(tot_lfct ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, family = "quasipoisson")

# f13 <- lme(log1p(tot_lfct) ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich), data = oak_2014, random = ~1|plotid)
# f13 <- glmer(tot_lfct ~ scale(tmi) + scale(d2c) + scale(elevation) + scale(hrs_14_20) + scale(os_rich) + (1|plotid), data = oak_2014, family = "poisson")
summary(f13) # tmi; p = 0.2562

f14 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "binomial")
chat <- deviance(f14)/df.residual(f14)
QAIC(update(f14, family = x.quasibinomial), chat = chat)
f14 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct), data = oak_2014, family = "quasibinomial")
# f14 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tmi) + scale(d2c) + scale(hrs_14_20) + scale(os_rich) + scale(tot_lfct) + (1|plotid), data = oak_2014, family = "binomial")
summary(f14) # tmi; p = 0.7633

f15 <- lm(log1p(os_rich) ~ hrs_14_20 + avg_psi + d2c + elevation + tmi, data = oak_2014)
# f15 <- lme(log1p(os_rich) ~ hrs_14_20 + avg_psi + d2c + elevation + tmi, data = oak_2014, random = ~1|plotid)
summary(f15) # hrs_14_20; p = 0.1039

# Calculate C-statistic
pvalues <- c(summary(f1)$tTable[2,5], summary(f2)$tTable[2,5], summary(f3)$tTable[2,5], summary(f4)$coefficients[2,4], summary(f5)$coefficients[2,4], summary(f6)$coefficients[2,4], summary(f7)$coefficients[2,4], summary(f8)$coefficients[2,4], summary(f9)$coefficients[2,4], summary(f10)$coefficients[2,4], summary(f11)$coefficients[2,4], summary(f12)$coefficients[2,4], summary(f13)$coefficients[2,4], summary(f14)$coefficients[2,4], summary(f15)$coefficients[2,4])

cstat <- -2 * sum(log(pvalues))
cstat # 69.18
chisq.test(c(cstat,30))
qchisq(pvalues, df = 30)
chisq.test(cbind(pvalues, qchisq(pvalues, df = 30)))
```

This C-statistic is much larger than the degrees of freedom, so I'm not confident in the conditional independencies of the structural model being met for the 2014 data. In fact, based on the C-test value from the earlier call to `shipleys.test` on these data this value is significantly different.

The models testing for conditional independence indicate direct effects of PSI and elevation on oak infection, as well as a direct effect of elevation on symptomatic leaf count. This is indicated by the p-values showing strong statistical significance in the relationship between these variables. Below I have generated a new path model that accounts for the unassumed direct effects, which means they become assumed direct effects.

```{r oak path 2}
oak_path2 <- DAG(
      tmi ~ elevation,
      os_rich ~ tmi,
      hrs_14_20 ~ elevation + d2c + avg_psi + tmi,
      tot_lfct ~ hrs_14_20 + os_rich + d2c + elevation,
      inf_oak_ct ~ tot_lfct + avg_psi + os_rich + hrs_14_20 + d2c + elevation
      )
isAcyclic(oak_path2)
bu_oak_path2 <- basiSet(oak_path2)
bu_oak_path2

shipley.test(oak_path2, cov(select(oak_2014, elevation, tmi, os_rich, hrs_14_20, d2c, avg_psi, tot_lfct, inf_oak_ct)), n = 168)

plotGraph(oak_path2)
```

This means commenting out models `f6` (oak ~ PSI), `f12` (oak ~ elevation), and `f11` (leaf count ~ elevation) in the `pvalues` summary.

```{r recalculate c-statistic}
pvalues <- c(
      summary(f1)$tTable[2,5], summary(f2)$tTable[2,5], summary(f3)$tTable[2,5],
      summary(f4)$coefficients[2,4], summary(f5)$coefficients[2,4], 
             # summary(f6)$coefficients[2,4], 
      summary(f7)$coefficients[2,4], summary(f8)$coefficients[2,4],
      summary(f9)$coefficients[2,4], summary(f10)$coefficients[2,4],
      # summary(f11)$coefficients[2,4], 
      # summary(f12)$coefficients[2,4], 
      summary(f13)$coefficients[2,4], summary(f14)$coefficients[2,4], summary(f15)$coefficients[2,4])

cstat <- -2 * sum(log(pvalues))
cstat # 36.56767
chisq.test(c(cstat,30))
```
I think this would be evidence for wanting/needing to use the repeated measures approach across all the data to capture interannual variation in the relationships.

I am continuing with fitting the models to estimate the path coefficients for 2014 data based on this redrawn path model.

```{r estimate path coefficients 2014}
# f0 <- fitted(mlme1, level = 0)# Values from population model
# f1 <- fitted(mlme1, level = 1)# Within beach fitted values

# fit1_2014 <- lm(tmi ~ scale(elevation), data = oak_2014)
fit1_2014 <- lm(log(tmi) ~ scale(elevation), data = oak_2014) # best model
# fit1_2014 <- lme(log(tmi) ~ scale(elevation), data = oak_2014, random = ~1|plotid)
summary(fit1_2014)
par(mfrow = c(2,2))
plot(fit1_2014)

# fit2_2014 <- lm(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2014)
# fit2_2014 <- lme(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2014, random = ~1|plotid) # best model
fit2_2014 <- glm(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2014, family = "poisson")
chat <- deviance(fit2_2014)/df.residual(fit2_2014)
QAIC(update(fit2_2014, family = x.quasipoisson), chat = chat)
fit2_2014 <- glm(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi), data = oak_2014, family = "quasipoisson")
# fit2_2014 <- glmer(hrs_14_20 ~ scale(elevation) + scale(d2c) + scale(avg_psi) + scale(tmi) + (1|plotid), data = oak_2014, family = "poisson")
summary(fit2_2014)
plot(fit2_2014)

# fit3_2014 <- lm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + scale(elevation), data = oak_2014)
# fit3_2014 <- lm(log1p(tot_lfct) ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + scale(elevation), data = oak_2014)
fit3_2014 <- glm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + scale(elevation), data = oak_2014, family = "poisson")
(chat <- deviance(fit3_2014) / df.residual(fit3_2014))
x.quasipoisson<-function(...){
  res<-quasipoisson(...)
  res$aic<-poisson(...)$aic
  res
}
library(MuMIn)
QAIC(update(fit3_2014, family = x.quasipoisson), chat = chat) # 178.3
fit3_2014 <- glm(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + scale(elevation), data = oak_2014, family = "quasipoisson") # best model
# fit3_2014 <- glmer(tot_lfct ~ scale(hrs_14_20) + scale(os_rich) + scale(d2c) + scale(elevation) + (1|plotid), data = oak_2014, family = "poisson")
summary(fit3_2014)

# fit4_2014 <- lm((inf_oak_ct/(inf_oak_ct+uninf_oak_ct)) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c) + scale(elevation) + scale(avg_psi), data = oak_2014)
par(mfrow = c(2,2))
plot(fit4_2014)

fit4_2014 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c) + scale(elevation) + scale(avg_psi), data = oak_2014, family = "binomial")
(chat <- deviance(fit4_2014) / df.residual(fit4_2014))
x.quasibinomial<-function(...){
  res<-quasibinomial(...)
  res$aic<-binomial(...)$aic
  res
}
library(MuMIn)
QAIC(update(fit4_2014, family = x.quasibinomial), chat = chat)
fit4_2014 <- glm(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c) + scale(elevation) + scale(avg_psi), data = oak_2014, family = "quasibinomial")

# fit4_2014 <- glmer(cbind(inf_oak_ct, uninf_oak_ct) ~ scale(tot_lfct) + scale(os_rich) + scale(hrs_14_20) + scale(d2c) + (1|plotid), data = oak_2014, family = "binomial") # best model
summary(fit4_2014)

# fit5_2014 <- lm(os_rich ~ tmi, data = oak_2014); AIC(fit5_2014)
fit5_2014 <- lm(log(os_rich) ~ tmi, data = oak_2014); AIC(fit5_2014)
# fit5_2014 <- lme(os_rich ~ tmi, data = oak_2014, random = ~1|plotid)
# fit5_2014 <- lme(log(os_rich) ~ tmi, data = oak_2014, random = ~1|plotid)
summary(fit5_2014)
```
